\documentclass[conference]{IEEEtran}

\IEEEoverridecommandlockouts

\usepackage{setspace}
\usepackage{enumerate}
\usepackage{cite}
\usepackage{times}
\usepackage{url}
\usepackage{graphicx}
%\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{color}

\input{entity_centric_kb_pop_defs}
\begin{document}
\title{An Entity-centric Approach for Overcoming \\Knowledge Graph Sparsity}
\author{
\IEEEauthorblockN{
Manjunath Hegde,
Partha Talukdar
}
\IEEEauthorblockA{Department~of~Computational~and~Data~Sciences\\
Indian Institute of Science, Bangalore, India\\
manjunath@ssl.serc.iisc.in,
ppt@cds.iisc.ac.in
}
}
\maketitle

\begin{abstract}

Automatic construction of knowledge graphs (KGs) from unstructured text has received considerable attention in recent research, resulting in the construction of several KGs with 
millions of entities (nodes) and facts (edges) among them. Unfortunately, such KGs tend to be severely sparse in terms of number of facts known for a \emph{given} entity, i.e., have low 
\emph{knowledge density}. For example, the NELL KG consists of only 1.34 facts per entity. Unfortunately, such low knowledge density makes it challenging to use  such KGs in real-world 
applications. In contrast to \emph{best-effort} extraction paradigms followed in the construction of such KGs, in this project we argue in favor of \systemfull{} (\system{}), an \emph{entity-centric}
KG population framework, to alleviate the low knowledge density problem in existing KGs. By using \system{}, we are able to increase NELL's knowledge density 
by a factor of 7.7 at 75.5\% accuracy. Additionally, we are also able to extend the ontology discovering new relations and entities. 
\end{abstract}

\input{sections/intro}
\input{sections/related}
\input{sections/results}
\input{sections/method}
\input{sections/experiments}
\input{sections/conclusion}
\section*{Acknowledgment}
I would like to thank Dr. Partha Talukdar for his valuable guidance and support throught the project.
Special thanks to Tushar Nagarajan for building the CNN model and helping me throught the relation mapping process.
All the other members of the Machine and Language Learning (MALL) lab friends for their suggestions and timely help.
I thank MALL lab and Computational and Data Science Department for providing Computational facilities.

\bibliographystyle{IEEEtran}
\bibliography{template}

\end{document}

